---
title: "AnalyzeGraysAnatomyNetwork"
author: "GuyGo and Ofri Masad"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
setwd("E:/Dropbox/Ofri & Guy/DS_again/hw3")
ga.data <- read.csv('ga_edgelist.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
g <- simplify(g)
```


# Network Analysis:
### Reading the data
The data is a csv files containing the graph edges of greys anatomy characters sexual relations.
And edge is represented by couple: {From, To}
```{r read_data, cache=TRUE}
head(ga.data)
```
### Data exploration:
#### Relations:
let's look on all the characters we got.
```{r relations, cache=TRUE}
V(g)$name
```
#### Number of Connections between characters:
```{r number_of_relations, cache=TRUE}
summary(g)
```

### Data-visualization:
#### Basic representation:
```{r basic, cache=TRUE}
g$layout <- layout.fruchterman.reingold(g)
plot(g)
```  

#### Degree score:
```{r degree, cache=TRUE}
degr.score <- degree(g)
degr.score
V(g)$size <- degree(g) * 3 
plot(g)
```

#### Closeness centrality:
```{r closeness_cent, cache=TRUE}
clo <- closeness(g) 
V(g)$color <- "gray"
V(g)$size <- clo*5000
V(g)$label <- V(g)$name
plot(g)
clo
which.max(clo)
```  

torres is the most central by Closeness


#### Betweeness centrality.
```{r betweeness_cent, cache=TRUE}
btw <- betweenness(g) 
V(g)$color <- "gray"
V(g)$size <- btw/4
V(g)$label <- V(g)$name
plot(g)
btw
which.max(btw)
```  

sloan is the most central by Betweeness

#### Eigenvector centrality.
```{r eigenvector_cent, cache=TRUE}
eig <- centr_eigen(g)
V(g)$color <- "gray"
V(g)$size <- eig$vector*15
V(g)$label <- V(g)$name
plot(g)
eig$vector
V(g)[which.max(V(g)$size)]
```  

karev is the most central by Eigenvector

#### Community strucure via short random walks
```{r random_walk_community, cache=TRUE}
fc <- walktrap.community(g)
memb <- membership(fc)
plot(g, vertex.size=5, vertex.label=V(g)$name,vertex.color=memb+1, asp=FALSE)
#number of communities and they size
table(memb)
#the modularity
modularity(fc)
```  


#### Girvan-Newman community detection algorithm
```{r Girvan_Newman_community, cache=TRUE}
gnc <- edge.betweenness.community(g, directed=FALSE)
memb2 <- membership(gnc)
plot(g, vertex.size=5, vertex.label=V(g)$name,vertex.color=memb2+1, asp=FALSE)
#number of communities and they size
table(memb2)
#the modularity
modularity(gnc)
```  


### Insights:
1. two hot guys leads in the number of sexual relations with other characters  
2. torres is bi-sexual